
With the \tB{\emph{generative} approach we create a joint model of the form $\prob{y,\bm{x}}$, and
then to condition on $\bm{x}$, thereby deriving $\prob{y|\bm{x}}$}.\\
Alternatively, \tB{fitting directly a model of the form $\prob{y|\bm{x}}$ is a \emph{
discriminative} approach}.

\begin{itemize}
    \item \emph{Easy to fit}: generative classifiers is usually very easy
    \item \emph{Fit classes separately?}: in a generative classifier we estimate the parameters 
        of each class conditional density independently
    \item \emph{Handle missing features easily?}: in a generative classifier there is a natural way
        to handle missing data: $\prob{\bm{x}_{i},r_{i}|\bm{\theta},\bm{\phi}} = \prob{r_{i}|\bm{
        x}_{i},\bm{\phi}}\prob{\bm{x}_{i}|\bm{\theta}}$ where $\bm{\phi}$ are the parameters
        controlling whether the item is observed or not. Missing completely at random (MCAR): $\prob{
        r_{i}|\bm{x}_{i},\bm{\phi}} = \prob{r_{i}|\bm{x}^{0}_{i}|\bm{\phi}}$, missing at random 
        (MAR): $\prob{r_{i}|\bm{x}_{i},\bm{\phi}} = \prob{r_{i}|\bm{x}^{0}_{i},\bm{\phi}}$
    \item \emph{Can handle unlabeled training data?}: Fairly easy to using generative models
    \item \emph{Symmetric in inputs and outputs?}: We can run a generative model "backward" and 
        infer probable inputs given the output by computing $\prob{\bm{x}|y}$
    \item \emph{Can handle feature preprocessing?}: discriminative methods allow to preprocess the
        input in arbitrary ways, by replacing $\bm{x}$ with $\phi(\bm{x})$
    \item \emph{Well-calibrated probabilities?}: discriminative models are usually better calibrated
        in terms of their probability estimates.
\end{itemize}


\section{Classification}
\input{chapters/3_classical_learning/01_supervised_learning/1_classification.tex}

\section{Regression}
\input{chapters/3_classical_learning/01_supervised_learning/2_regression.tex}

\section{Classification and Regression}
\input{chapters/3_classical_learning/01_supervised_learning/3_both.tex}

\section{Model Selection}
\input{chapters/3_classical_learning/01_supervised_learning/4_model_selection.tex}

\section{Regularization}
\input{chapters/3_classical_learning/01_supervised_learning/5_regularization.tex}
