\section{Inspection} 
Detect unexpected behavior in the data.
\begin{itemize}
    \item \textbf{Data profiling}: summary statistics about the data, see \href{https://github.com/ydataai/ydata-profiling}{\textit{ydata-profiling}} in Python.
    \item \textbf{Visualizations}: visualize the data using statistical metrics, see
        \href{https://plotly.com/python/}{\textit{plotly}}
    \item \textbf{Software packages}: to note and check the constraints regarding the data
        see \href{https://pypi.org/project/pydeequ/}{\textit{pydeequ}}
\end{itemize}

\section{Cleaning} 
Fix or remove anomalies discovered in the above phase.
\begin{itemize}
    \item \textbf{Irrelevant Data}: ask to the expert what can be the unnecessary columns,
        check them and remove them if they are not useful.
    \item \textbf{Duplicates}
    \item \textbf{Type conversion}: make sure the appropriate data type is associated with
        a given column.
    \item \textbf{Syntax errors}: white spaces, pad strings \dots
    \item \textbf{Standardize}: same unit across the dataset, same pattern for text.
    \item \textbf{Scaling/Transformation}: in order to compare different scores for 
        example.
    \item \textbf{Normalization}: useful for some statistical methods.
    \item \textbf{Missing values}: 
        \begin{itemize}
            \item Drop: only if the missing values in a column rarely and randomly occur.
            \item Impute: many methods,  
                \begin{itemize}
                    \item \textit{mean} is relevant when data is not skewed
                    \item \textit{median} otherwise
                    \item \textit{hot-deck} imputes from a randomly selected similar record
                    \item \textit{polynomial interpolation} approximate the data with a polynomial 
                    \item \textit{linear regression} imputes from prediction 
                    \item \textit{k-nearest} imputes depending on a set of closet observations
                \end{itemize}
            \item Flag: let the missing value as it is.
        \end{itemize}
    \item Outliers: Remove outliers only if they are harmful for the chosen model.
    \item In-record \& cross-datasets errors: fix non-consistent situations like married 
        kids, quantity being different of the one when we compute using other columns.
\end{itemize}

\section{Verifying}
Check correctness of the cleaning phase.
\section{Reporting} 
Report about changes made, using one of the software summarising the data quality for 
example.
